### 2016-10-01 lin-correctness.tex

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:lin-correctness-adv}
\begin{figure}[tp]
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B_1^{\calO}(S, \pubaux)}$\\
%$S \getsr A$\\
$\calC \gets \emptyset$; $\err \gets 0$\\
%$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(\pubaux)$\\
When $A$ asks $\TestOracle(\qry_x)$:\\
\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
\nudge $\calC \gets \calC \cup x$\\
\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
\nudge if $a \neq \qry_x(S)$ then \\
\nudge \nudge $\err \gets \err + 1$\\
\nudge Return~$a$\\
When $A$ halts: \\
\nudge if $\err  < r$ then Return 0\\
\nudge Return 1\\

\medskip
\oracle{$\HashOracle(x)$}\\
for $i \in \{1,2,\ldots,k\}$\\
\nudge $v_i \gets F_{K}(\langle 1,x \rangle) + i \cdot \calO(\langle 2,x \rangle) \bmod m$\\
Return ${v_1,v_2,\ldots,v_k}$
}
{
$\adversaryv{B_2^{\calO}(S, \pubaux)}$\\
%$S \getsr A$\\
$\calC \gets \emptyset$; $\err \gets 0$\\
%$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(\pubaux)$\\
When $A$ asks $\TestOracle(\qry_x)$:\\
\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
\nudge $\calC \gets \calC \cup x$\\
\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
\nudge if $a \neq \qry_x(S)$ then \\
\nudge \nudge $\err \gets \err +1$\\
\nudge Return~$a$\\
When $A$ halts: \\
\nudge if $\err  < r$ then Return 0\\
\nudge Return 1

\medskip
\oracle{$\HashOracle(x)$}\\
$a \getsr [m]$\\
if $T[x] \neq \undefined$\\
\nudge $a \gets T[x]$\\
$T[x] \gets a$\\
for $i \in \{1,2,\ldots,k\}$\\
\nudge $v_i \gets \calO(\langle 1,x \rangle) + i\cdot a$\\
Return ${v_1,v_2,\ldots,v_k}$
}
}
\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively for the
proof of Theorem~\ref{thm:lin-correctness}.}\label{fig:lin-correctness-adv}
\fixme{fix caption and Crefs}
\end{figure}

@@

In $\game{3}(A)$, we replace the random functions used in
$\HashOracle$ (in $\game{2}(A)$) with lazy sampling of elements from
$[m]$.  This change does not alter the behavior of the oracle, as the
random functions are (by the no-pointless-queries assumption on~$A$) always called on a new
value of~$x$.
%
Also, the $\Test$ oracle now sets $\bad$ to $\true$ if the
queries indexed by the set $\mathcal{I}$ fail to be false-positives,
or if any of the remaining queries are false-positives. It can be
observed that the $\bad$ flag has no impact on the output of the
$\Test$, nor does it affect  the value returned
by~$\game{3}$. Thus we have $\Prob{\game{2}(A)=1} =
\Prob{\game{3}(A)=1}$ and
\[
\Prob{\game{3}(A)=1 \wedge \game{3}(A): \neg\bad} = \Prob{\game{3}(A)=1} \Prob{\game{3}(A) : \neg\bad}%\label{eq:1} \\
\]

@@

Before continuing the proof, a bit of intuition for the introduction
of the $\bad$-flag in games~$\game{3},\game{4}$.   Intuitively, if the index
set~$\mathcal{I}$ exactly predicts which of the $\Test$ queries will be
false-positives (and, conversely, which will not be), then a
zero-query FP-finding adversary can ``guess'' which of~$A$'s queries require it
to return 1 when simulating the $\Test$, and which require it to
return 0.  In this way, no queries ever actually need to be made.
Moving to a zero-query setting will allow us to connect to classical
results on the FP-rate of Bloom filters; more in a moment.

Now, consider $\Prob{\game{3}(A) : \neg\bad}$.  The indicated event
happens iff the $r$-set~$\calI$ contains exactly the indices of
$\Test$-queries that are false-positives.  Since the value
of~$\bad$ does not alter the responses of~$\Test$, $\err$'s update
and the set~$\calI$ are independent.
Thus $\bad$ remains $\false$ after~$A$ halts with probability
$1/\binom{q}{r}$, and we have 
\begin{equation*}
\Prob{\game{4}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{3}(A)=1}
\end{equation*}

Recall that adversary~$A$ wins $\ExpCorrect{\setprim_{\mathrm{lin}},r}{}$ by finding~$r$ false positives. We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive. % We can also assume that every point in $\calZ$ has already been queried to $\Test$.  This latter assumption is not without loss, but can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$. 
%
%Under these assumptions,
So, if $\game{4}(A)=1$, then there is a zero-query adversary~$D$ that finds~$r$ false positives against $\tilde{\setprim}_{\mathrm{lin}}$, which is $\setprim_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.  We give this~$D$ in Figure~\ref{fig:lin-correctness-zq-adv}. Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives; it simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ false-positives. It must be noted that, by the no-pointless queries assumption and the fact that the hash functions in $D$ are instantiated with random functions, $\pubaux$ is information theoretically independent of elements not in $S$. Thus we have
$\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{\setprim}_{\mathrm{lin}},r}{D} = 1}$.

@@

\medskip
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Games $\game{0}$-$\game{4}$ for the
proof of Theorem~\ref{thm:lin-correctness}.}
\label{fig:lin-correctness-games}
\fixme{fix caption and Crefs}
\end{figure}

>>>>

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:lin-correctness-adv}
\begin{figure}[tp]
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B_1^{\calO}}$\\
$S \getsr A$\\
$\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(\pubaux)$\\
When $A$ asks $\TestOracle(\qry_x)$:\\
\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
\nudge $\calC \gets \calC \cup x$\\
\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
\nudge if $a \neq \qry_x(S)$ then \\
\nudge \nudge $\err \gets \err + 1$\\
\nudge Return~$a$\\
When $A$ halts: \\
\nudge if $\err  < r$ then Return 0\\
\nudge Return 1\\

\medskip
\oracle{$\HashOracle(x)$}\\
for $i \in \{1,2,\ldots,k\}$\\
\nudge $v_i \gets F_{K}(\langle 1,x \rangle) + i \cdot \calO(\langle 2,x \rangle) \bmod m$\\
Return ${v_1,v_2,\ldots,v_k}$
}
{
$\adversaryv{B_2^{\calO}}$\\
$S \getsr A$\\
$\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(\pubaux)$\\
When $A$ asks $\TestOracle(\qry_x)$:\\
\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
\nudge $\calC \gets \calC \cup x$\\
\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
\nudge if $a \neq \qry_x(S)$ then \\
\nudge \nudge $\err \gets \err +1$\\
\nudge Return~$a$\\
When $A$ halts: \\
\nudge if $\err  < r$ then Return 0\\
\nudge Return 1

\medskip
\oracle{$\HashOracle(x)$}\\
$a \getsr [m]$\\
if $T[x] \neq \undefined$\\
\nudge $a \gets T[x]$\\
$T[x] \gets a$\\
for $i \in \{1,2,\ldots,k\}$\\
\nudge $v_i \gets \calO(\langle 1,x \rangle) + i\cdot a$\\
Return ${v_1,v_2,\ldots,v_k}$
}
}
\caption{Adversary $B_1$ simulating $\game{0}(A)$ and $\game{1}(A)$, and $B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$  respectively for the proof of Theorem~\ref{thm:lin-correctness}.}\label{fig:lin-correctness-adv}
%\fixme{fix caption and Crefs}
\end{figure}

@@

In $\game{3}(A)$, we replace the random functions used in
$\HashOracle$ (in $\game{2}(A)$) with lazy sampling of elements from
$[m]$.  This change does not alter the behavior of the oracle, as the
random functions are (by the no-pointless-queries assumption on~$A$) always called on a new
value of~$x$.
%
Also, the $\TestOracle$ oracle now sets $\bad$ to $\true$ if the
queries indexed by the set $\mathcal{I}$ fail to be false-positives,
or if any of the remaining queries are false-positives. It can be
observed that the $\bad$ flag has no impact on the output of the
$\TestOracle$, nor does it affect  the value returned
by~$\game{3}$. Thus we have $\Prob{\game{2}(A)=1} =
\Prob{\game{3}(A)=1}$ and
\[
\Prob{\game{3}(A)=1 \wedge \game{3}(A): \neg\bad} = \Prob{\game{3}(A)=1} \Prob{\game{3}(A) : \neg\bad}%\label{eq:1} \\
\]

@@

Before continuing the proof, a bit of intuition for the introduction
of the $\bad$-flag in games~$\game{3},\game{4}$.   Intuitively, if the index
set~$\mathcal{I}$ exactly predicts which of the $\TestOracle$ queries will be
false-positives (and, conversely, which will not be), then a
zero-query FP-finding adversary can ``guess'' which of~$A$'s queries require it
to return 1 when simulating the $\TestOracle$, and which require it to
return 0.  In this way, no queries ever actually need to be made.
Moving to a zero-query setting will allow us to connect to classical
results on the FP-rate of Bloom filters; more in a moment.

Now, consider $\Prob{\game{3}(A) : \neg\bad}$.  The indicated event
happens iff the $r$-set~$\calI$ contains exactly the indices of
$\TestOracle$-queries that are false-positives.  Since the value
of~$\bad$ does not alter the responses of~$\TestOracle$, $\err$'s update
and the set~$\calI$ are independent.
Thus $\bad$ remains $\false$ after~$A$ halts with probability
$1/\binom{q}{r}$, and we have 
\begin{equation*}
\Prob{\game{4}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{3}(A)=1}
\end{equation*}

Recall that adversary~$A$ wins $\ExpCorrect{\setprim_{\mathrm{lin}},r}{}$ by finding~$r$ false positives. We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive. % We can also assume that every point in $\calZ$ has already been queried to $\Test$.  This latter assumption is not without loss, but can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$. 
%
%Under these assumptions,
So, if $\game{4}(A)=1$, then there is a zero-query adversary~$D$ that finds~$r$ false positives against $\tilde{\setprim}_{\mathrm{lin}}$, which is $\setprim_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.  We give this~$D$ in Figure~\ref{fig:lin-correctness-zq-adv}. Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives; it simulates the~$\TestOracle$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ false-positives. It must be noted that, by the no-pointless queries assumption and the fact that the hash functions in $D$ are instantiated with random functions, $\pubaux$ is information theoretically independent of elements not in $S$. Thus we have
$\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{\setprim}_{\mathrm{lin}},r}{D} = 1}$.

@@

\medskip
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Games $\game{0}$-$\game{4}$ for the
proof of Theorem~\ref{thm:lin-correctness}.}
\label{fig:lin-correctness-games}
%\fixme{fix caption and Crefs}
\end{figure}
